# Data

## Sources

Describe the data sources: who is responsible for collecting the data? How is it collected? If there were a choice of options, explain how you chose. (It's ok if there some repetition with the previous chapter. Chapter 2 will reflect your thinking at the time of the proposal and Chapter 3 will represent the state of the project when it is complete.)

Provide some basic information about the data: types of variables, number of records, etc.

Describe any issues / problems with the data, either known or that you discover.

(suggested: approximately 1 page)

```{r}
library(dplyr)
library(tibble)
library(tidyr)
library(ggplot2)
library(forcats)
```

```{r warning=False}
# data <- readr::read_csv("/Users/ricole/Desktop/Leetcode-Note/2019_Iowa_Liquor_Sales_sample.csv", show_col_types = FALSE)
data <- readr::read_csv("https://raw.githubusercontent.com/RicoXu727/Leetcode-Note/main/2019_Iowa_Liquor_Sales_sample.csv", show_col_types = FALSE)
```

```{r}
drop <- c("Invoice/Item Number","Address", "Store Location", "Volume Sold (Liters)")
subdata = data[,!(names(data) %in% drop)]
```

```{r}
colSums(is.na(subdata)) %>%
  sort(decreasing = TRUE)
```

```{r}
set.seed(10)
x <- sampledData <- sample(1:nrow(subdata), 1000)
headdata <- subdata[x, ]
```

```{r}
colnames(headdata)[2] ="StNum"
colnames(headdata)[3] ="StName"
colnames(headdata)[6] ="CoNum"
colnames(headdata)[8] ="Cat"
colnames(headdata)[9] ="CatName"
colnames(headdata)[10] ="VenNum"
colnames(headdata)[11] ="VenName"
colnames(headdata)[12] ="ItNum"
colnames(headdata)[13] ="ItDes"
colnames(headdata)[15] ="BV"
colnames(headdata)[16] ="SBC"
colnames(headdata)[17] ="SBR"
colnames(headdata)[18] ="BS"
colnames(headdata)[19] ="Sale"
colnames(headdata)[20] ="VS"
# headdata <- headdata %>% 
#             rename("Store Number" = "StNum","Store Name" = "StName", "County Number" = "CoNum", "Category" = "Cat", "Category Name" = "CatName","Vendor Number" = "VenNum","Vendor Name" = "VenName", "Item Number" = "ItNum","Item Description" = "ItDes","Bottle Volumn (ml)" = "BV", "State Bottle Cost" = "SBC","Bottle Sold" = "BS","Sale (Dollars)" = "Sale","Volume Sold (Gallons)" = "VS")
```

```{r}
tidydata <- headdata %>% 
    rownames_to_column("id") %>% 
    gather(key, value, -id) %>%
    mutate(missing = ifelse(is.na(value), "yes", "no"))
```

```{r}
ggplot(tidydata, aes(x = key, y = fct_rev(id), fill = missing)) +
  geom_tile(color = "white") +
  ggtitle("mtcars with NAs added") +
  ylab('') + 
  scale_fill_viridis_d() + # discrete scale
  theme_bw()
```

```{r}
newdata <- na.omit(subdata)
```

## Cleaning / transformation

Describe the process of getting the data into a form in which you could work with it in R if relevant. If your code does not lend itself to being including in the `.Rmd`  file, provide a link to the folder or file(s) that contain(s) that code. (If your data did not require any cleaning or transformation before beginning EDA simply state that.)

(suggested: approximately 1/2 page)

```{r}

```

## Missing value analysis

Describe any patterns you discover in missing values. If no values are missing, graphs should still be included showing that.

(suggested: 2 graphs plus commentary)

```{r}

```
